Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2019-02-22 paper/tidy-missing-data-paper.Rmd
update reference data to point to zenodo dataset
update date

---
title: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
author: "Nicholas Tierney, Department of Econometrics and Business Statistics, Monash University, **Corresponding author (nicholas.tierney@gmail.com)** \\newline Dianne Cook, Department of Econometrics and Business Statistics, Monash University"
date: "September 6, 2018"
toc: false
bibliography: tidy-missing-data-paper.bib
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
csl: jcgs.csl
---

@@

To illustrate the methods, data on housing for the city of Melbourne from January 28, 2016 to March 17, 2018 is used. The data was compiled by scraping weekly property clearance data [@kaggle2018]. There are `r scales::number(nrow(housing), big.mark = ",")` properties, and `r ncol(housing)` variables in the dataset. The variables include the type of real estate (town house, unit, house), suburb, method of selling, number of rooms, price, real estate agent, date of sale, and the distance from the Central Business District (CBD).

>>>>

---
title: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
author: "Nicholas Tierney, Department of Econometrics and Business Statistics, Monash University, E774, Menzies Building Monash University, Clayton, 3168, Victoria, Australia **Corresponding author (nicholas.tierney@gmail.com)** \\newline Dianne Cook, Department of Econometrics and Business Statistics, Monash University"
date: "February 23, 2019"
toc: false
bibliography: tidy-missing-data-paper.bib
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
csl: jcgs.csl
---

@@

To illustrate the methods, data on housing for the city of Melbourne from January 28, 2016 to March 17, 2018 is used. The data was compiled by scraping weekly property clearance data [@Kaggle-2018-data]. There are `r scales::number(nrow(housing), big.mark = ",")` properties, and `r ncol(housing)` variables in the dataset. The variables include the type of real estate (town house, unit, house), suburb, method of selling, number of rooms, price, real estate agent, date of sale, and the distance from the Central Business District (CBD).
